---
title: "Untitled"
author: "Jan Luca Schnatz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
dependecies <- read_csv(here("Mastering_Shiny/dependecies.csv")) %>% pull(packages)
pacman::p_load(char = dependecies)

```

```{r}
server <- function(input, output, session) {}
```

# Inputs

## Common Structure

- `inputId`: id to connect front end with backend
  - example: ui: "name" -> server: input$name
  - must be a single string with only letters, numbers and underscores
  - must be unique
- `label`: Human-readable label for the control
- `value`: set default value (if possible)

```{r}
# Example:
sliderInput(
  inputId = "min",
  label = "Limit (minimum)",
  value = 50,
  min = 0,
  max = 100
)
```

## Free Text

- `textInput()`: small amounts of text
- `passwordInput()`: passwords
- `textAreaInput()`: paragraphs

```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  passwordInput("password", "What's your password?"),
  textAreaInput("story", "Tell me about yourself", rows = 3)
)

ui

```

## Numeric Inputs

- `numericInput()`: numeric constrained text box
- `sliderInput()`: slider

```{r}
ui <- fluidPage(
  numericInput("num", "Number one", value = 0, min = 0, max = 100),
  sliderInput("num2", "Number two", value = 50, min = 0, max = 100),
  sliderInput("rng", "Range", value = c(10, 20), min = 0, max = 100)
)

shinyApp(ui, server)

```

## Dates

- `dateInput()`: single date
- `dateRangeInput()`: date range

```{r}

ui <- fluidPage(
  dateInput("dob", "When were you born?", language = "de"),
  dateRangeInput("holiday", "When do you want to go on vacation next?", language = "de")
)

shinyApp(ui, server)

```

## Limited Choices

- `selectInput()`: drop-down MC (multiple possible)
- `radioButtons()`: small buttons MC (multiple impossible)
- `checkboxGroupInput()`: checkbox (multiple possible)
- `checkboxInput()`: single checbox (yes/no)

```{r}
letters_sample <- letters[1:5]

ui <- fluidPage(
  selectInput(
    inputId = "select",
    label = "This is the selectInput",
    choices = letters_sample,
    multiple = TRUE # multiple selection
    ),
  radioButtons(
    inputId = "radio",
    label = "This is the radioButton",
    choices = letters_sample
  ),
  checkboxGroupInput(
    inputId = "checkboxgroup",
    label = "This is a checkboxGroupInput",
    choices = letters_sample
  ),
  checkboxInput(
    inputId = "checkbox",
    label = "Shutdown?"
  )
)

shinyApp(ui, server)

```

## File uploads

- `fileInput()`: allow user to upload file

```{r}
ui <- fluidPage(
  fileInput("upload", NULL)
)
ui
```

## Action buttons

- `actionButton()`
- `actionLink()`

Action buttons can be paired with `observeEvent()` or `eventReactive()` in the server function.

```{r}

ui <- fluidPage(
  actionButton("click", "Click me!"),
  actionButton("drink", "Drink me!", icon = icon("cocktail")),
  actionLink("link", label = "google.com")
)
ui

```

## Exercices

1. When space is at a premium, it’s useful to label text boxes using a placeholder that appears inside the text entry area. How do you call textInput() to generate the UI below?

```{r}
textInput("text", label = NULL, placeholder = "Your name")
```

2. Carefully read the documentation for sliderInput() to figure out how to create a date slider, as shown below.

```{r}
ui <- fluidPage(sliderInput("slider", "When should we deliver?",
            min = as.Date("2020-09-16", "%Y-%m-%d"), 
            max = as.Date("2020-09-23", "%Y-%m-%d"), 
            value = as.Date("2020-09-17", "%Y-%m-%d"),
            timeFormat = "%Y-%m-%d"))

shinyApp(ui, server)
```

# Outputs

## Text
## Tables
## Plots
## Downloads
## Exercices
